Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome

### 2016-05-23 submission/Sze_Obesity_PeerJ_2016.Rmd
add Pat data LME results pt3

***Z-Score Normalization Pooled Analysis***

Using the third approach with Z-score normalization we found that there was no significant difference in the Shannon diversity between the obese and non-obese group (P-value = `r format(round(combZHTtest$p.value, 2), nsmall=2)`) [Figure 5A]. Additionally,  we found that the there was also no significant difference in B/F ratio, using the Z-score normalization, between obese and non-obese individuals (P-value = `r format(round(combZLogBFTtest$p.value, 2), nsmall=2)`) [Figure 5B].

>>>>

***Linear Mixed-Effect models for Pooled Analysis***

Using the third approach which utilizes a linear mixed-effect model to control for the effect of study on the Shannon diversity  we found that there was a significant difference between the obese and non-obese groups (P-value = `r format(round(alpha_composite.summary['shannon', 'composite_p'], 4), nsmall=4)`) [Figure 5A]. Additionally,  there was also a significant difference in obseverd richness (P-value = `r format(round(alpha_composite.summary['sobs', 'composite_p'], 9), nsmall=9)`.  However, we found that the there was no significant difference in evenness (P-value = `r format(round(alpha_composite.summary['shannoneven', 'composite_p'], 2)), nsmall=2)`, Bacteroidetes (P-value = `r format(round(alpha_composite.summary['bacteroidetes', 'composite_p'], 2)), nsmall=2)`), Firmicutes (P-value = `r format(round(alpha_composite.summary['firmicutes', 'composite_p'], 2)), nsmall=2)`), and B/F ratio (P-value = `r format(round(alpha_composite.summary['bf_ratio', 'composite_p'], 2)), nsmall=2)`using this approach, between obese and non-obese individuals [Figure 5B].
